Simulation for Correlation Motif

### 2017-09-16 analysis/Simulation.Rmd
wflow_publish("analysis/Simulation.Rmd")
wflow_publish("Simulation.Rmd")

## Model framework

The framework of Correlation Motif model is based on my write-up document and supplementary matrials by $Wei$ $and$ $Ji$ (2015). In $Wei$ $and$ $Ji$ (2015), they implemented an EM algorithm and introduced priors for both $\pi$ and $Q$. As a result, their iterative formulas for new $\pi$ and new $Q$ are:

@@

>>>>

## Model Framework

The framework of Correlation Motif model is based on my [write-up document](../paper/Cormotif.pdf) and supplementary matrials by [$Wei$ $and$ $Ji$ (2015)][wj]. In $Wei$ $and$ $Ji$ (2015), they implemented an EM algorithm and introduced priors for both $\pi$ and $Q$. As a result, their iterative formulas for new $\pi$ and new $Q$ are:

@@

## Session information.

```{r info}
print(sessionInfo())
```

[wj]: https://doi.org/10.1093/biostatistics/kxu038
